---
title: "Extortion in Mexico: Who pays and why?"
author: "Patricio R. Estevez Soto"
email: "patricio.estevez.14@ucl.ac.uk"
date: "05/05/2018"
output:
  md_document:
    variant: "markdown"
pandoc_args: "--smart"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment="",
                      cache=TRUE,
                      #dev=c("png", "CairoPDF"),
                      error=TRUE)
options(knitr.kable.NA = '---')
```

# Introduction

This document contains the script and results for a research project on extortion against businesses in Mexico.

Previous research has found that extortion against businesses is acutely concentrated on a few businesses who experience more than half of all extortion incidents in the country as repeat extortion victimizations. That project found that the rate at which businesses suffer extortion is mostly determined by their characteristics---such as their age, whether they are a restaurant, the number of corruption incidents they have suffered, and their size---and to a lesser extent, to the characteristics of the state where they are located---which include the state homicide rate and other unmeasured between-state differences.

Nonetheless, that research did not consider that most extortion victims do not comply with extortion demands. Thus this project aims to explore the distribution of successful extortion incidents, and identify the incident, victim and area characteristics associated with a higher likelihood of complying with extortion.

The incident-level characteristics that will be explored are:

- month
- time of day
- number of offenders
- victim's relationship to the offender
- use of a weapon
- type of weapon
- use of violence
- whether the incident was reported to the authorities (MP + other)
- type of extortion
- what was requested
- retaliation against business for not complying
- whether the victim complied with the extortion

The victim-level characteristics are:
- business type
- business age
- business size
- Victim of corruption
- number of corruption victimizations, repeat corruption victim
- number of extortion victimizations
- repeat extortion victim

Area-level characteristics:
- State
- State homicides
- State population (control)
Add more stuff here

# Set up, data input and pre-process

## Session info

We first check details of the session and system, and for reproducibility, we set the random seed.

```{r session, cache=FALSE}
starttime <- proc.time()
date()
sessionInfo()
set.seed(42)
options(scipen=0)
```

## Load packages and functions

Next we load the packages that we will use.

```{r packages}

#library(Cairo)
#library(glmmTMB)
library(victim)
library(tidyverse)
library(downloader)
library(sandwich)
library(lmtest)
library(arsenal)

read.dbf <- foreign::read.dbf

kable <- knitr::kable
melt <- reshape2::melt
select <- dplyr::select
Anova <- car::Anova

sessionInfo()

```


Load custom functions

```{r functions}
mylog <- function(x, center = FALSE){
    if(min(x) <= 0) {tlog <- log1p}
    else {tlog <- log}

    logx <- tlog(x)

    if(isTRUE(center))
    {
        logx <- logx - tlog(mean(x))
    }

    if(is.numeric(center)){
        logx <- logx - tlog(center)
    }

    return(logx)

}

vif <- function(form, data, family = "binomial"){
    if(!is_formula(form)) {form <- formula(form)}

    lmmod <- glm(form, data = data,  family = family)

    vifs <- car::vif(lmmod)

    return(vifs)
}

add_stars <- function(pval, alpha = c(0.001, 0.01, 0.05))
{
    ifelse(pval < alpha[1], "***", ifelse(pval < alpha[2], "**",
        ifelse(pval < alpha[3], "*", "")))
}

summaryCL <- function(m, clusterid, conf.level = 0.95, boots = FALSE, R = 400, ...){
    if(isFALSE(boots))
    {
        robust_vcov <- sandwich::vcovCL(m, cluster = clusterid)
    } else
    {
        robust_vcov <- sandwich::vcovBS(m, cluster = clusterid, R, ...)
    }

    rob_coef <- lmtest::coeftest(m, vcov. = robust_vcov)
    rob_confint <- lmtest::coefci(m, level = conf.level, vcov. = robust_vcov)

    results <- cbind(rob_coef, rob_confint)
    results <- data.frame(results)

    names(results) <- c("estimate", "SE", "z.value", "p.value", "ci.low", "ci.high")

    results$sig <- add_stars(results[,4])

    waldt <- lmtest::waldtest(m, vcov = robust_vcov, test = "Chisq")

    results_list <- list(coefs = results, clusterid = clusterid, wald = waldt, vcov = robust_vcov)

    class(results_list) <- "summaryCL"

    return(results_list)

}


print.summaryCL <- function(summaryCL.object){
    print(summaryCL.object[-4])
}

vcov.summaryCL <- function(summaryCL.object){
    summaryCL.object$vcov
}


# predictive accuracy function

accuracy <- function(mod){

    nm <- mod$model

    # Naive Guess
    t1 <- table(nm[,1])
    pt1 <- prop.table(t1)
    ng <- round(max(pt1) * 100, 3)

    # Predictive accuracy
    nm$predicted <- round(predict(mod,type = "response"))

    confusion <- table(nm[,1], nm$predicted)

    predaccu <- round(sum(diag(confusion)) / sum(confusion) * 100, 3)

    return(list(accuracy = predaccu, naive = ng))

}

mysummary <- function(m){
    print(summary(m))
    print(car::vif(m))
    print(logLik(m))
    print(waldtest(m, test = "Chisq"))
    print(accuracy(m))
    print(car::Anova(m))
}

mkbin <- function(x,n = 0) ifelse(x > n, 1, 0)

```

## Load data

We first load and arrange the area and victim level data

```{r test-setting}

### Change if not in testing settings
#params <- list(test = TRUE)
if(params$test){
    download("https://raw.githubusercontent.com/prestevez/datahouse/master/enve2014cuest_ciega_2014.dbf",
                      destfile = "enve2014cuest_ciega_2014.dbf", mode = "wb")
    download("https://raw.githubusercontent.com/prestevez/datahouse/master/enve2014delitos_ciega_2014.dbf",
                 destfile = "enve2014delitos_ciega_2014.dbf", mode = "wb")
}

list.files()

```


```{r victim-level}
cat_entidades <- read.csv("https://raw.githubusercontent.com/prestevez/datahouse/master/cat_entidades.csv", head=TRUE)
state_level_data <- read.csv("https://raw.githubusercontent.com/prestevez/datahouse/master/state_level_data_2013.csv", header=TRUE)
state_level_data <- merge(state_level_data,
                          cat_entidades, by="CVE_ENT", all.x=TRUE)
scode <- read.csv("https://raw.githubusercontent.com/prestevez/datahouse/master/secode.csv", head=TRUE)
scode$Code <- scode$Code*10000


enve_all <- read.dbf("enve2014cuest_ciega_2014.dbf")



# Prepare data for analysis
# Selecting only the relevant variables
enve_test <- data.frame(extortions=as.integer(as.character(enve_all$P26_10)))
enve_test$extortion_victim <- enve_all$P25_10
enve_test$extortions[enve_test$extortion_victim == 2] <- 0
summary(enve_test$extortions)

enve_test$extortions[is.na(enve_test$extortions)] <- 0

summary(enve_test$extortions)

table(enve_test$extortions)

enve_test$rep_extortion_victim <- mkbin(enve_test$extortions, 1)

enve_test$rep_extortions <- enve_test$extortions
enve_test$rep_extortions[enve_test$rep_extortions > 0] <- enve_test$rep_extortions[enve_test$rep_extortions > 0] - 1

summary(enve_test$rep_extortions)

table(enve_test$rep_extortions)

enve_test$CVE_UNICA <- as.integer(as.character(enve_all$ID_CONSECU))

enve_test$bribes <- as.integer(as.character(enve_all$P33))
summary(enve_test$bribes)

# 4 bribe cats
enve_test$bribe1 <- enve_all$P29_1
enve_test$bribe2 <- enve_all$P30_1
enve_test$bribe3 <- enve_all$P31_1
enve_test$bribe4 <- enve_all$P32_1

enve_test$bribes[with(enve_test,
                        bribe1 == 2 &
                        bribe2 == 2 &
                        bribe3 == 2 &
                        bribe4 == 2)] <- 0

summary(enve_test$bribes)

enve_test$bribes[is.na(enve_test$bribes)] <- 0

enve_test$bribe_victim <- mkbin(enve_test$bribes, 0)

table(enve_test$bribe_victim)

enve_test$rep_bribe <- mkbin(enve_test$bribes, 1)

table(enve_test$rep_bribe)

enve_test$bribe_cats <- factor(enve_test$bribes)
levels(enve_test$bribe_cats) <- c(0, 1, 2, rep("3+",
                                            length(levels(enve_test$bribe_cats)) - 3))
summary(enve_test$bribe_cats)

enve_test$CVE_ENT <- as.integer(as.character(enve_all$CVE_ENT))

enve_test$size <- enve_all$ID_ESTRATO
levels(enve_test$size) <- c("Large", "Medium", "Small", "Micro")

enve_test$sector <- enve_all$SECTOR_FIN

# subsector
enve_test$tempsub <- as.integer(as.character(enve_all$P1_1B))
enve_test$subsector <- cut(enve_test$tempsub, scode$Code, right=FALSE)
levels(enve_test$subsector) <- scode$Sector
enve_test$subsector <- droplevels(enve_test$subsector)
enve_test$subsector <- relevel(enve_test$subsector, ref="Retail")
levels(enve_test$subsector)

enve_test$subsector_safe <- enve_test$subsector

enve_test$subsector <- as.character(enve_test$subsector)

# Must remember to exclude utilities from analysis

enve_test$subsector[enve_test$subsector %in%
                      c("Mining",
                        "Construction")] <- "Other industry"

# Must remember to exclude Corporate from analysis

enve_test$subsector[enve_test$subsector %in%
                      c("Media",
                        "Maintenance",
                        "Other",
                        "Finance",
                        "Health",
                        "Leisure",
                        "Education",
                        "Prof. services",
                        "Real estate")] <- "Other serv."


enve_test$subsector <- as.factor(enve_test$subsector)
enve_test$subsector <- relevel(enve_test$subsector, ref="Retail")
levels(enve_test$subsector)

summary(enve_test$subsector)

enve_test$years <- 2013 - as.numeric(as.character(enve_all$P3))
summary(enve_test$years)

intyears <- classInt::classIntervals(enve_test$years, 5, style="quantile")
enve_test$yearsquant <- cut(enve_test$years, intyears$brks, right=TRUE,
                            include.lowest = TRUE)

enve_test <- merge(enve_test, state_level_data, by="CVE_ENT", all.x=TRUE)

length(enve_test$extortions[is.na(enve_test$extortions)])

length(enve_test$bribes[is.na(enve_test$bribes)])

## enve_test$extortions[is.na(enve_test$extortions)] <- 0
## enve_test$bribes[is.na(enve_test$bribes)] <- 0

summary(enve_test)

# Exclude Corporate and Utilitites

nrow(enve_test) # should be 28179

enve_test %>%
    filter(subsector != "Utilities") %>%
    filter(subsector != "Corporate") -> enve_test_2

enve_test_2$subsector <- droplevels(enve_test_2$subsector)

levels(enve_test_2$subsector)

enve_test_2$subsector_safe <- droplevels(enve_test_2$subsector_safe)
levels(enve_test_2$subsector_safe)

nrow(enve_test_2) # should be 28161

enve_test <- enve_test_2
nrow(enve_test)

summary(enve_test)

```

Next we load incident-level data:

```{r incident-level}


enve_incidents_all <- read.dbf("enve2014delitos_ciega_2014.dbf")

# Selecting only those relevant for extortion (code 10)

enve_incidents_all$delito <- as.integer(as.character(enve_incidents_all$ID_DELITO))

enve_incidents <- enve_incidents_all[enve_incidents_all$delito == 10,]

# Selecting those relevant for our study

incident_df <- data.frame(CVE_UNICA=as.integer(as.character(enve_incidents$ID_CONSECU)))

incident_df$month <- as.numeric(as.character(enve_incidents$M1_1))

incident_df$delito <- enve_incidents$delito

incident_df$n_offenders <- enve_incidents$M1_8
summary(incident_df$n_offenders)

levels(incident_df$n_offenders) <- c(1:6, "DK/DA")
summary(incident_df$n_offenders)

incident_df$n_offenders_NA <-  incident_df$n_offenders
incident_df$n_offenders_NA[is.na(incident_df$n_offenders)] <- "DK/DA"
summary(incident_df$n_offenders_NA)

incident_df$n_offenders_old <- incident_df$n_offenders_NA
levels(incident_df$n_offenders_NA) <- c(1:3, "4+", "4+", "4+", "DK/DA")
summary(incident_df$n_offenders_NA)

incident_df$uk_n_offenders <- incident_df$n_offenders_NA

levels(incident_df$uk_n_offenders)[1:4] <- "known"

incident_df$n_offenders_num <- enve_incidents$M1_8
summary(incident_df$n_offenders_num)

levels(incident_df$n_offenders_num) <- c(1:6, 0)
summary(incident_df$n_offenders_num)

incident_df$n_offenders_num[is.na(incident_df$n_offenders_num)] <- 0
incident_df$n_offenders_num <- as.numeric(as.character(incident_df$n_offenders_num))
table(incident_df$n_offenders_num)

incident_df$n_offenders_num <- incident_df$n_offenders_num - 1


## Data imputation for missing variables?

incident_df$rel_offenders <- enve_incidents$M1_11
levels(incident_df$rel_offenders) <- c("Known", "Known",
                                       "Known", "Known",
                                       "Total stranger", "DK/DA")
incident_df$rel_offenders <- relevel(incident_df$rel_offenders, ref="Total stranger")
summary(incident_df$rel_offenders)

incident_df$rel_offenders_NA <- incident_df$rel_offenders
incident_df$rel_offenders_NA[is.na(incident_df$rel_offenders_NA)] <- "DK/DA"
summary(incident_df$rel_offenders_NA)

incident_df$had_weapon <- enve_incidents$M1_13
levels(incident_df$had_weapon) <- c("Yes", "No", "DK/DA")
incident_df$had_weapon <- relevel(incident_df$had_weapon, ref="No")
summary(incident_df$had_weapon)

incident_df$had_weapon_NA <- incident_df$had_weapon
incident_df$had_weapon_NA[is.na(incident_df$had_weapon_NA)] <- "DK/DA"
summary(incident_df$had_weapon_NA)

incident_df$extortion_type <- as.character(enve_incidents$M5_1)
incident_df$extortion_type <- as.factor(incident_df$extortion_type)
levels(incident_df$extortion_type) <- c("Remote", "Remote", "Street",
                                        "Premises", "Cobro de piso", "Other")
levels(incident_df$extortion_type)

summary(incident_df$extortion_type)

incident_df$extortion_type_bin <- as.character(enve_incidents$M5_1)
incident_df$extortion_type_bin <- as.factor(incident_df$extortion_type_bin)
levels(incident_df$extortion_type_bin) <- c("Remote", "Remote", "In person",
                                        "In person", "In person", "Other")
levels(incident_df$extortion_type_bin)

summary(incident_df$extortion_type_bin)

# Extortion bin w/o Cobro de piso
incident_df$extortion_type_wocp <- as.character(enve_incidents$M5_1)
incident_df$extortion_type_wocp <- as.factor(incident_df$extortion_type_wocp)
levels(incident_df$extortion_type_wocp) <- c("Remote", "Remote", "In person",
                                        "In person", "Other", "Other")
levels(incident_df$extortion_type_wocp)

summary(incident_df$extortion_type_wocp)

incident_df$complied <- enve_incidents$M5_3
levels(incident_df$complied) <-  c("Yes", "No", "DK/DA")
incident_df$complied <- relevel(incident_df$complied, ref="No")
summary(incident_df$complied)

incident_df$complied_bin <- enve_incidents$M5_3
levels(incident_df$complied_bin) <-  c("Yes", "No", NA)
incident_df$complied_bin <- relevel(incident_df$complied_bin, ref="No")
summary(incident_df$complied_bin)

incident_df$complied_bin_NA <- incident_df$complied_bin
incident_df$complied_bin_NA[is.na(incident_df$complied_bin_NA)] <- "No"
summary(incident_df$complied_bin_NA)

incident_df <- subset(incident_df, extortion_type != "Other")
incident_df$extortion_type <- droplevels(incident_df$extortion_type)

# Remember to subset out "other" obs from extortion_type_wocp
incident_df$extortion_type_bin <- droplevels(incident_df$extortion_type_bin)

summary(incident_df)
```

Next we merge both incident-level and victim-level tables.

```{r incident-victim-merge}
enve_incvic <- merge(incident_df, enve_test, by="CVE_UNICA")

nrow(enve_incvic)
nrow(incident_df)
```


# Models


```{r subset-no-NA}

## datasets with no NA values first.

nacols <- colnames(enve_incvic)[colSums(is.na(enve_incvic)) > 0]

nonacols <- names(enve_incvic)[!(names(enve_incvic) %in% nacols)]

enve_incvic %>%
    select(nonacols) -> enve_nona

summary(enve_nona)
nrow(enve_nona)
nrow(enve_nona[complete.cases(enve_nona),])
nrow(enve_nona[complete.cases(enve_incvic),])

## Data structure

"number of incidents"
nrow(enve_nona)

"incidents per business"
table(table(enve_nona$CVE_UNICA))
enve_nona %>%
    count(CVE_UNICA) %>%
    summarise(min(n),
              max(n),
              mean(n),
              n())

"number of incidents per state"
enve_nona %>%
    count(CVE_ENT) %>%
    summarise(min(n),
              mean(n),
              max(n),
              n())

"number of businesses per state"
enve_nona %>%
    count(CVE_ENT, CVE_UNICA) %>%
    count(CVE_ENT) %>%
    summarise(min(n),
              mean(n),
              max(n))

```

```{r state-level-means}

mean_bribes <- mean(state_level_data$bribes_abvic)
mean_bribes

mean_armas <- mean(state_level_data$armas)
mean_armas

mean_drogas <- mean(state_level_data$drogas)
mean_drogas

mean_poblacion <- mean(state_level_data$poblacion)
mean_poblacion

mean_N <- mean(state_level_data$N)
mean_N

mean_General <- mean(state_level_data$General)
mean_General

mean_Derecho <- mean(state_level_data$Derecho)
mean_Derecho


```


First the canonical model with the state level variables identified in JQC manuscript.

# EDA

```{r tableby_eda}
my_controls <- tableby.control(numeric.test = "kwt", cat.test = "chisq")


my_labels <- list(
  extortion_type = "Extortion type",
  extortion_type_bin = "Extortion type (binary)",
  extortion_type_wocp = "Extortion type (Other: piso)",
  n_offenders_NA = "Num. offenders",
  n_offenders_old = "Num. offenders (all cat.)",
  had_weapon_NA = "Had weapon",
  extortions = "Extortion concentration",
  bribes = "Corruption incidence",
  subsector = "Business type",
  subsector_safe = "Business type (all cat.)",
  size = "Business size",
  yearsquant = "Age (quintiles)",
  years = "Age"
)

#
#table_two <- tableby(continent ~ .,
#  data = gapminder,
#  control = my_controls
#)
#
#summary(table_two,
#  labelTranslations = my_labels,
#  title = "Summary Statistic of Gapminder Data"
#)
#


desc_formula <-  ~ extortion_type +
                        extortion_type_bin +
                        extortion_type_wocp +
                        n_offenders_NA +
                        n_offenders_old +
                        had_weapon_NA +
                        extortions +
                        bribes +
                        subsector +
                        subsector_safe +
                        size +
                        yearsquant +
                        years


desc_table <- tableby(desc_formula, data  = enve_nona,
                control = my_controls)

summary(desc_table,
            labelTranslations = my_labels,
            pfootnote = TRUE)

desc_formula2 <-  update(desc_formula, complied_bin_NA ~ .)


desc_table2 <- tableby(desc_formula2, data  = enve_nona,
                        control = my_controls)

summary(desc_table2,
            labelTranslations = my_labels,
            pfootnote = TRUE)

desc_formula3 <-  update(desc_formula, extortion_type ~ . -
                                        extortion_type -
                                        extortion_type_bin -
                                        extortion_type_wocp)


desc_table3 <- tableby(desc_formula3, data  = enve_nona,
                        control = my_controls)

summary(desc_table3,
            labelTranslations = my_labels,
            pfootnote = TRUE)

desc_formula4 <-  update(desc_formula3, extortion_type_bin ~ .)


desc_table4 <- tableby(desc_formula4, data  = enve_nona,
                        control = my_controls)

summary(desc_table4,
            labelTranslations = my_labels,
            pfootnote = TRUE)


desc_formula5 <-  update(desc_formula3, extortion_type_wocp ~ .)


desc_table5 <- tableby(desc_formula5,
                        data = subset(enve_nona, extortion_type_wocp != "Other"),
                        control = my_controls)

summary(desc_table5,
            labelTranslations = my_labels,
            pfootnote = TRUE)

## Extortion type and include compliance

desc_formula6 <-  update(desc_formula3, complied_bin_NA ~ .)


# EDA for remote extortions
desc_table6 <- enve_nona %>%
  filter(extortion_type == "Remote") %>%
  tableby(desc_formula6,
          data = .,
          control = my_controls)

summary(desc_table6,
            labelTranslations = my_labels,
            pfootnote = TRUE)

# EDA for street extortions
desc_table7 <- enve_nona %>%
  filter(extortion_type == "Street") %>%
  tableby(desc_formula6,
          data = .,
          control = my_controls)

summary(desc_table7,
            labelTranslations = my_labels,
            pfootnote = TRUE)


# EDA for Premises extortions
desc_table8 <- enve_nona %>%
  filter(extortion_type == "Premises") %>%
  tableby(desc_formula6,
          data = .,
          control = my_controls)

summary(desc_table8,
            labelTranslations = my_labels,
            pfootnote = TRUE)

# EDA for Cobro de piso extortions
desc_table9 <- enve_nona %>%
  filter(extortion_type == "Cobro de piso") %>%
  tableby(desc_formula6,
          data = .,
          control = my_controls)

summary(desc_table9,
            labelTranslations = my_labels,
            pfootnote = TRUE)


# EDA for In person extortions
desc_table10 <- enve_nona %>%
  filter(extortion_type_bin == "In person") %>%
  tableby(desc_formula6,
          data = .,
          control = my_controls)

summary(desc_table10,
            labelTranslations = my_labels,
            pfootnote = TRUE)



# EDA for In person wocp extortions
desc_table11 <- enve_nona %>%
  filter(extortion_type_wocp == "In person") %>%
  tableby(desc_formula6,
          data = .,
          control = my_controls)

summary(desc_table11,
            labelTranslations = my_labels,
            pfootnote = TRUE)
```





Fit the models



```{r models-1}


compliance_formula <- complied_bin_NA ~ extortion_type +
                                        n_offenders_NA +
                                        had_weapon_NA +
                                        mylog(extortions) +
                                        mylog(bribes) +
                                        subsector +
                                        size +
                                        yearsquant +
                                        mylog(bribes_abvic, TRUE) +
                                        mylog(armas, TRUE) +
                                        mylog(drogas, TRUE) +
                                        mylog(poblacion, TRUE) +
                                        mylog(N, TRUE) +
                                        scale(General, scale = FALSE) +
                                        scale(Derecho, scale = FALSE)

m1 <- glm(formula = compliance_formula, data = enve_nona, family = binomial())  

summary(m1)
vif(m1, data = enve_nona) 

logLik(m1)


m1_step <- step(m1, direction = "both")

summary(m1_step)
logLik(m1_step)

waldtest(m1_step, test = "Chisq")

waldtest(m1_step, m1, test = "Chisq")

car::vif(m1_step)

lrtest(m1_step, m1)
Anova(m1)
Anova(m1_step)

accuracy(m1)
accuracy(m1_step)

```

Use Robust Clustered Errors


```{r clustered-SE-asym}

# m1, m1step, m1_inc,  m1_bus, m1_state, m1_inc_bus

#### Asymptotic Cluster SE
## Individual-level clustering

cluster_form <- ~ CVE_UNICA + CVE_ENT

m1CL <- summaryCL(m1, cluster_form)
m1CL

m1_stepCL <- summaryCL(m1_step, cluster_form)
m1_stepCL

waldtest(m1_step, m1, test = "Chisq", vcov = vcov(m1CL))


```



# Per extortion type

Fit the same models as above (m1 and a reduced m1) fur subsets per extortion type

- Remote


```{r models-remote}

compliance_formula2 <- complied_bin_NA ~ n_offenders_NA +
                                        had_weapon_NA +
                                        mylog(extortions) +
                                        mylog(bribes) +
                                        subsector +
                                        size +
                                        yearsquant +
                                        mylog(bribes_abvic, TRUE) +
                                        mylog(armas, TRUE) +
                                        mylog(drogas, TRUE) +
                                        mylog(poblacion, TRUE) +
                                        mylog(N, TRUE) +
                                        scale(General, scale = FALSE) +
                                        scale(Derecho, scale = FALSE)

enve_remote <- filter(enve_nona, extortion_type == "Remote")

m1_remote <- glm(formula = compliance_formula2, 
                 data = enve_remote, 
                 family = binomial())  

summary(m1_remote)
vif(m1_remote, data = enve_nona) 

logLik(m1_remote)


m1_remote_step <- step(m1_remote, direction = "both")

summary(m1_remote_step)
logLik(m1_remote_step)

waldtest(m1_remote_step, test = "Chisq")

waldtest(m1_remote_step, m1_remote, test = "Chisq")

car::vif(m1_remote_step)

lrtest(m1_remote_step, m1_remote)
Anova(m1_remote)
Anova(m1_remote_step)

accuracy(m1_remote)
accuracy(m1_remote_step)

# Robust SE

m1_remoteCL <- summaryCL(m1_remote, cluster_form)
m1_remoteCL

m1_remote_stepCL <- summaryCL(m1_remote_step, cluster_form)
m1_remote_stepCL

waldtest(m1_remote_step, m1_remote, test = "Chisq", vcov = vcov(m1_remoteCL))

# using m1_step terms

m1_remote_step2 <- update(m1_step, 
                             . ~ . - extortion_type,
                             data = enve_remote)


summary(m1_remote_step2)
logLik(m1_remote_step2)

waldtest(m1_remote_step2, test = "Chisq")

waldtest(m1_remote_step2, m1_remote, test = "Chisq")

car::vif(m1_remote_step2)

lrtest(m1_remote_step2, m1_remote)
Anova(m1_remote)
Anova(m1_remote_step2)

accuracy(m1_remote)
accuracy(m1_remote_step2)

# Robust SE



m1_remote_step2CL <- summaryCL(m1_remote_step2, cluster_form)
m1_remote_step2CL

waldtest(m1_remote_step2, m1_remote, test = "Chisq", vcov = vcov(m1_remoteCL))




```


- premises


```{r models-premises}

enve_premises <- filter(enve_nona, extortion_type == "Premises")

m1_premises <- glm(formula = compliance_formula2, 
                 data = enve_premises, 
                 family = binomial())  

summary(m1_premises)
vif(m1_premises, data = enve_nona) 

logLik(m1_premises)


m1_premises_step <- step(m1_premises, direction = "both")

summary(m1_premises_step)
logLik(m1_premises_step)

waldtest(m1_premises_step, test = "Chisq")

waldtest(m1_premises_step, m1_premises, test = "Chisq")

car::vif(m1_premises_step)

lrtest(m1_premises_step, m1_premises)
Anova(m1_premises)
Anova(m1_premises_step)

accuracy(m1_premises)
accuracy(m1_premises_step)

# Robust SE

m1_premisesCL <- summaryCL(m1_premises, cluster_form)
m1_premisesCL

m1_premises_stepCL <- summaryCL(m1_premises_step, cluster_form)
m1_premises_stepCL

waldtest(m1_premises_step, m1_premises, test = "Chisq", vcov = vcov(m1_premisesCL))

# using m1_step terms

m1_premises_step2 <- update(m1_step, 
                             . ~ . - extortion_type,
                             data = enve_premises)


summary(m1_premises_step2)
logLik(m1_premises_step2)

waldtest(m1_premises_step2, test = "Chisq")

waldtest(m1_premises_step2, m1_premises, test = "Chisq")

car::vif(m1_premises_step2)

lrtest(m1_premises_step2, m1_premises)
Anova(m1_premises)
Anova(m1_premises_step2)

accuracy(m1_premises)
accuracy(m1_premises_step2)

# Robust SE



m1_premises_step2CL <- summaryCL(m1_premises_step2, cluster_form)
m1_premises_step2CL

waldtest(m1_premises_step2, m1_premises, test = "Chisq", vcov = vcov(m1_premisesCL))





```

- street



```{r models-street}

enve_street <- filter(enve_nona, extortion_type == "Street")

m1_street <- glm(formula = compliance_formula2, 
                 data = enve_street, 
                 family = binomial())  

summary(m1_street)
vif(m1_street, data = enve_nona) 

logLik(m1_street)


m1_street_step <- step(m1_street, direction = "both")

summary(m1_street_step)
logLik(m1_street_step)

waldtest(m1_street_step, test = "Chisq")

waldtest(m1_street_step, m1_street, test = "Chisq")

car::vif(m1_street_step)

lrtest(m1_street_step, m1_street)
Anova(m1_street)
Anova(m1_street_step)

accuracy(m1_street)
accuracy(m1_street_step)

# Robust SE

m1_streetCL <- summaryCL(m1_street, cluster_form)
m1_streetCL

m1_street_stepCL <- summaryCL(m1_street_step, cluster_form)
m1_street_stepCL

waldtest(m1_street_step, m1_street, test = "Chisq", vcov = vcov(m1_streetCL))

# using m1_step terms

m1_street_step2 <- update(m1_step, 
                             . ~ . - extortion_type,
                             data = enve_street)


summary(m1_street_step2)
logLik(m1_street_step2)

waldtest(m1_street_step2, test = "Chisq")

waldtest(m1_street_step2, m1_street, test = "Chisq")

car::vif(m1_street_step2)

lrtest(m1_street_step2, m1_street)
Anova(m1_street)
Anova(m1_street_step2)

accuracy(m1_street)
accuracy(m1_street_step2)

# Robust SE



m1_street_step2CL <- summaryCL(m1_street_step2, cluster_form)
m1_street_step2CL

waldtest(m1_street_step2, m1_street, test = "Chisq", vcov = vcov(m1_streetCL))





```

- cobro de piso



```{r models-piso}
enve_piso <- filter(enve_nona, extortion_type == "Cobro de piso")

m1_piso <- glm(formula = compliance_formula2, 
                 data = enve_piso, 
                 family = binomial())  

summary(m1_piso)
vif(m1_piso, data = enve_nona) 

logLik(m1_piso)


m1_piso_step <- step(m1_piso, direction = "both")

summary(m1_piso_step)
logLik(m1_piso_step)

waldtest(m1_piso_step, test = "Chisq")

waldtest(m1_piso_step, m1_piso, test = "Chisq")

car::vif(m1_piso_step)

lrtest(m1_piso_step, m1_piso)
Anova(m1_piso)
Anova(m1_piso_step)

accuracy(m1_piso)
accuracy(m1_piso_step)

# Robust SE

m1_pisoCL <- summaryCL(m1_piso, cluster_form)
m1_pisoCL

m1_piso_stepCL <- summaryCL(m1_piso_step, cluster_form)
m1_piso_stepCL

waldtest(m1_piso_step, m1_piso, test = "Chisq", vcov = vcov(m1_pisoCL))

# using m1_step terms

m1_piso_step2 <- update(m1_step, 
                             . ~ . - extortion_type,
                             data = enve_piso)


summary(m1_piso_step2)
logLik(m1_piso_step2)

waldtest(m1_piso_step2, test = "Chisq")

waldtest(m1_piso_step2, m1_piso, test = "Chisq")

car::vif(m1_piso_step2)

lrtest(m1_piso_step2, m1_piso)
Anova(m1_piso)
Anova(m1_piso_step2)

accuracy(m1_piso)
accuracy(m1_piso_step2)

# Robust SE



m1_piso_step2CL <- summaryCL(m1_piso_step2, cluster_form)
m1_piso_step2CL

waldtest(m1_piso_step2, m1_piso, test = "Chisq", vcov = vcov(m1_pisoCL))





```


- Inperson (agg)

```{r models-in-person}

enve_inperson <- filter(enve_nona, extortion_type_bin == "In person")

m1_inperson <- glm(formula = compliance_formula2, 
                 data = enve_inperson, 
                 family = binomial())  

summary(m1_inperson)
vif(m1_inperson, data = enve_nona) 

logLik(m1_inperson)


m1_inperson_step <- step(m1_inperson, direction = "both")

summary(m1_inperson_step)
logLik(m1_inperson_step)

waldtest(m1_inperson_step, test = "Chisq")

waldtest(m1_inperson_step, m1_inperson, test = "Chisq")

car::vif(m1_inperson_step)

lrtest(m1_inperson_step, m1_inperson)
Anova(m1_inperson)
Anova(m1_inperson_step)

accuracy(m1_inperson)
accuracy(m1_inperson_step)

# Robust SE

m1_inpersonCL <- summaryCL(m1_inperson, cluster_form)
m1_inpersonCL

m1_inperson_stepCL <- summaryCL(m1_inperson_step, cluster_form)
m1_inperson_stepCL

waldtest(m1_inperson_step, m1_inperson, test = "Chisq", vcov = vcov(m1_inpersonCL))

# using m1_step terms

m1_inperson_step2 <- update(m1_step, 
                             . ~ . - extortion_type,
                             data = enve_inperson)


summary(m1_inperson_step2)
logLik(m1_inperson_step2)

waldtest(m1_inperson_step2, test = "Chisq")

waldtest(m1_inperson_step2, m1_inperson, test = "Chisq")

car::vif(m1_inperson_step2)

lrtest(m1_inperson_step2, m1_inperson)
Anova(m1_inperson)
Anova(m1_inperson_step2)

accuracy(m1_inperson)
accuracy(m1_inperson_step2)

# Robust SE



m1_inperson_step2CL <- summaryCL(m1_inperson_step2, cluster_form)
m1_inperson_step2CL

waldtest(m1_inperson_step2, m1_inperson, test = "Chisq", vcov = vcov(m1_inpersonCL))





```

- Inperson (agg) wocp


```{r models-in-person_wocp}

enve_inperson_wocp <- filter(enve_nona, extortion_type_wocp == "In person")

m1_inperson_wocp <- glm(formula = compliance_formula2, 
                 data = enve_inperson_wocp, 
                 family = binomial())  

summary(m1_inperson_wocp)
vif(m1_inperson_wocp, data = enve_nona) 

logLik(m1_inperson_wocp)


m1_inperson_wocp_step <- step(m1_inperson_wocp, direction = "both")

summary(m1_inperson_wocp_step)
logLik(m1_inperson_wocp_step)

waldtest(m1_inperson_wocp_step, test = "Chisq")

waldtest(m1_inperson_wocp_step, m1_inperson_wocp, test = "Chisq")

car::vif(m1_inperson_wocp_step)

lrtest(m1_inperson_wocp_step, m1_inperson_wocp)
Anova(m1_inperson_wocp)
Anova(m1_inperson_wocp_step)

accuracy(m1_inperson_wocp)
accuracy(m1_inperson_wocp_step)

# Robust SE

m1_inperson_wocpCL <- summaryCL(m1_inperson_wocp, cluster_form)
m1_inperson_wocpCL

m1_inperson_wocp_stepCL <- summaryCL(m1_inperson_wocp_step, cluster_form)
m1_inperson_wocp_stepCL

waldtest(m1_inperson_wocp_step, m1_inperson_wocp, test = "Chisq", vcov = vcov(m1_inperson_wocpCL))

# using m1_step terms

m1_inperson_wocp_step2 <- update(m1_step, 
                             . ~ . - extortion_type,
                             data = enve_inperson_wocp)


summary(m1_inperson_wocp_step2)
logLik(m1_inperson_wocp_step2)

waldtest(m1_inperson_wocp_step2, test = "Chisq")

waldtest(m1_inperson_wocp_step2, m1_inperson_wocp, test = "Chisq")

car::vif(m1_inperson_wocp_step2)

lrtest(m1_inperson_wocp_step2, m1_inperson_wocp)
Anova(m1_inperson_wocp)
Anova(m1_inperson_wocp_step2)

accuracy(m1_inperson_wocp)
accuracy(m1_inperson_wocp_step2)

# Robust SE



m1_inperson_wocp_step2CL <- summaryCL(m1_inperson_wocp_step2, cluster_form)
m1_inperson_wocp_step2CL

waldtest(m1_inperson_wocp_step2, m1_inperson_wocp, test = "Chisq", vcov = vcov(m1_inperson_wocpCL))





```

# Benchmark stats

```{r timing, cache=FALSE}
endtime <- proc.time()
time <- endtime - starttime
time

print(paste("the script took", round(time[3]/60,2),
              "minutes to run.", sep=" "))
```
